---
title: "Four Parameters Categorical"
author: "Faisal Jan"
format: html
execute: 
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
```

U.S Elections are beyond a competition between Republication and Democratic parties. Using the data set about US people’s voting result from American National Election Studies survey, I seek to understand the relationship between preference of men and women in 1992's Presidential election. However, the survey might contains false information of people who they voted.

$$
P(Y = k) = \frac{e^{\beta_{k0} + \beta_{k1} X_1 + \beta_{k2} X_2 + \cdots + \beta_{kn} X_n}}{\sum_{j=1}^{K} e^{\beta_{j0} + \beta_{j1} X_1 + \beta_{j2} X_2 + \cdots + \beta_{jn} X_n}}
$$

with $Y \sim \text{Multinomial}(\boldsymbol{\rho})$ where $\boldsymbol{\rho} = (\rho_1, \rho_2, \ldots, \rho_K)$ are the probabilities above.

$$
\begin{align*}
\log\left(\frac{\hat{P}(\text{Clinton})}{\hat{P}(\text{Bush})}\right) = 0.4554 - 0.2554 \cdot \text{Male} \\
\log\left(\frac{\hat{P}(\text{Perot})}{\hat{P}(\text{Bush})}\right) = -0.8519 + 0.4202 \cdot \text{Male}
\end{align*}
$$

```{r}
#| cache: true
nes_92 <- nes |> 
  filter(year == 1992) |> 
  select(sex, pres_vote) |> 
  drop_na() |> 
  mutate(pres_vote = as.factor(case_when(
    pres_vote == "Democrat" ~ "Clinton",
    pres_vote == "Republican" ~ "Bush",
    pres_vote == "Third Party" ~ "Perot",
  ))) 

fit_nes <- multinom_reg(engine = "nnet") |>
  fit(pres_vote ~ sex, data = nes_92)
```
